---
title: "Cleaning and Wrangling Data"
author: "Tasha Quintana"
date: "2023-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r load packages, warnings = FALSE, message = FALSE}
library(dplyr)
library(tidyr)
library(readr)
```


# Introduciton

About the data: This data was downloaded from [here](https://knb.ecoinformatics.org/view/df35b.304.2).

## Read data

```{r read data, warnings = FALSE, message = FALSE}

catch_original <- read_csv("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.302.1")

```

## Explore data

```{r explore, eval=FALSE, echo=FALSE}

colnames(catch_original)

head(catch_original)

summary(catch_original)

unique(catch_original$Year)

sort(unique(catch_original$Year))

sort(unique(catch_original$Region))

```

# Clean and reshape data

## Selecting and removing columns with `select()`

```{r select}

catch_data <- catch_original %>% 
  select(Region, Year, Chinook, Sockeye, Coho, Pink, Chum)

head(catch_data)

```

## Check column types

```{r checking}

glimpse(catch_data)

```

## Changing column types using mutate

```{r changing column types}

catch_clean <- catch_data %>%
  mutate(Chinook = as.numeric(Chinook))

head(catch_clean)

```

## Checking NA

```{r}

i <- which(is.na(catch_clean$Chinook))

catch_data[i,]

```

## Fixing Chinook column

```{r}
catch_clean <- catch_data %>% 
  mutate(Chinook = if_else(Chinook == "I", 
                           "1",
                           Chinook),
         Chinook = as.numeric(Chinook))

## Check
catch_clean[i,]

head(catch_clean)

```


## Reshape data

From wide to long

```{r wide to long}

catch_long <- catch_clean %>% 
  pivot_longer(cols = -c(Region, Year),
               names_to = "species",
               values_to = "catch")

head(catch_long)

```

From long to wide

```{r long to wide}

catch_wide <- catch_long %>% 
  pivot_wider(names_from = species, 
              values_from = catch)

head(catch_wide)

```

## Renaming column

```{r}

catch_long <- catch_long %>% 
  rename(catch_thousands = catch)

colnames(catch_long)

```

## Add a column using `mutate()`

```{r}

catch_long <- catch_long %>% 
  mutate(catch = catch_thousands*1000)

head(catch_long)


```


## Group by region

```{r}

mean_region <- catch_long %>% 
  group_by(Region) %>% 
  summarize(catch_mean = mean(catch))

head(mean_region)

n_region <- catch_long %>% 
  group_by(Region) %>% 
  summarize(abs_n = n())

head(n_region)

```


## Filtering by rows with `filter()`

```{r}

unique(catch_long$Region)

sse_catch <- catch_long %>% 
  filter(Region == "SSE")

head(sse_catch)


```

