---
title: "Introduction to RMarkdown"
author: "Tasha Quintana"
date: "2023-04-03"
output: 
  html_document:
    toc: true
    toc_float: true
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasha's example RMarkdown

Camila is *awesome*. Indeed she is awesomeness^2^. Subscripts are~sick~

Strikethroughs are also ~~awesome~~. It's a great idea to have a link to my [website](https://anastasiaquintana.com/)

------------------------------------------------------------------------

## Second section

This is the second section.

## Adding citations

Feedback loops are serious things [@quintana2021].

And Baja is a great place to study them [@quintana2021]

## Adding tables

| Veggie options   | Meat options         |
|------------------|----------------------|
| veggie burger    | weird meats          |

# R Code Chunk 1

```{r example}

heights_ft <- c(5.4, 5.4, 5.9)

coef <- 3.14

```

## Exercise new chunk

```{r friends}

names_friends <- c("Claire", "Liz", "Janet")

heights_friends <- c(5.3, 5.3, 5.2)

```

